Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-07-02 draft/accordionComplexSurfaces.tex
definition curve

\subsection{Accordion complex, slalom complex, and non-crossing complex}
Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.
%Let~$I$ denote the interior points and $B$ the blossom points.
We say that a $B$-arc is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
Note that no $B$-arc can cross an external $B$-arc.

@@

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ crosses a face~$f$ of~$\dissection$,
\begin{itemize}
\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,
\item there exists a marked points~$v$ shared by~$e_1$ and~$e_2$ such that~$v$ and~$f\dual$ lie on opposite sides of~$\alpha$ in~$f$.
\end{itemize}
\end{definition}

>>>>

\subsection{Accordion complex, slalom complex, and non-crossing complex}
Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.

\begin{definition}
A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
\end{definition}

%Let~$I$ denote the interior points and $B$ the blossom points.
We say that a $B$-arc is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
Note that no $B$-arc can cross an external $B$-arc.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.

@@

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ crosses a face~$f$ of~$\dissection$,
\begin{itemize}
\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,
\item $\alpha$, $e_1$ and~$e_2$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
\end{itemize}
\end{definition}

\begin{remark}
In Definition~\ref{def:accordion}, observe that
\begin{itemize}
\item the edges of~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ might coincide, see ...
\item the second condition is automatically satisfied if~$f\dual$ is not a puncture.
\end{itemize}
\end{remark}
